---
title: "Getting Started with kalshiR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with kalshiR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  eval      = FALSE   # Don't run chunks — no live API in CRAN checks
)
```

## Overview

`kalshiR` gives you a tidy R interface to the [Kalshi](https://kalshi.com)
prediction market exchange. You can:

- Browse markets, events, and series
- Pull live and historical price data
- View your portfolio balance and positions
- Place, amend, and cancel orders

This vignette covers installation, authentication setup, and your first API
calls. See the **Market Data** and **Trading** vignettes for deeper coverage.

---

## Installation

```{r install}
# Install from GitHub (until on CRAN)
# install.packages("pak")
pak::pkg_install("yourname/kalshiR")
```

---

## Authentication

Kalshi uses RSA asymmetric key authentication. Here's how to set it up:

### Step 1: Create an API key on Kalshi

1. Log in to [kalshi.com](https://kalshi.com) (or [demo.kalshi.co](https://demo.kalshi.co) for the demo environment).
2. Navigate to **Account & Security → API Keys → Create Key**.
3. Save the **private key** (`.key` file) somewhere secure on your machine.
4. Copy the **API Key ID** (it looks like a UUID).

### Step 2: Load your credentials in R

```{r auth}
library(kalshiR)

creds <- kalshi_auth(
  api_key_id       = "a952bcbe-ec3b-4b5b-b8f9-11dae589608c",  # your key ID
  private_key_path = "~/.kalshi/kalshi.key",                   # path to .key file
  env              = "production"   # or "demo" for the test environment
)

# Set globally — now all functions find credentials automatically
kalshi_set_auth(creds)
```

> **Security tip**: Never hard-code your API Key ID or key path in scripts
> you'll share. Use environment variables instead:

```{r auth-env}
# In your .Renviron file (run usethis::edit_r_environ() to open it):
# KALSHI_API_KEY=a952bcbe-ec3b-4b5b-b8f9-11dae589608c
# KALSHI_KEY_PATH=~/.kalshi/kalshi.key

creds <- kalshi_auth(
  api_key_id       = Sys.getenv("KALSHI_API_KEY"),
  private_key_path = Sys.getenv("KALSHI_KEY_PATH")
)
kalshi_set_auth(creds)
```

---

## Your First Requests

### Browse series

A **series** is a collection of related markets, such as "NYC Daily High
Temperature" or "Federal Reserve Rate Decision".

```{r series}
# Get metadata for a specific series
get_series("KXHIGHNY")

# List all series in the Economics category
get_series_list(category = "Economics")
```

### Browse markets

```{r markets}
# All currently open markets in the KXHIGHNY series
markets <- get_markets(series_ticker = "KXHIGHNY", status = "open")
markets

# A single market by its ticker
get_market("KXHIGHNY-23NOV07-T60")
```

### Check the orderbook

```{r orderbook}
# Top 5 price levels on each side
ob <- get_orderbook("KXHIGHNY-23NOV07-T60", depth = 5)
ob

# Implied probabilities
ob$implied_prob <- price_to_prob(ob$price_cents)
ob
```

### Get your account balance

```{r balance}
# Requires authentication
get_balance()
```

---

## Demo vs Production

The demo environment at `demo.kalshi.co` is a safe sandbox with fake money.
It mirrors the production API exactly, so it's ideal for testing your code.

```{r demo}
demo_creds <- demo_creds()

```

Pass `demo_creds` explicitly to any function, or call
`kalshi_set_auth(demo_creds)` to use it globally.

---

## Next Steps

- **`vignette("market-data")`** — deep dive into series, events, candlesticks,
  and historical data.
- **`vignette("trading")`** — placing orders, managing positions, and checking
  fills.
