---
title: "Market Data: Candlesticks, History, and Pagination"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Market Data: Candlesticks, History, and Pagination}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  eval      = FALSE   # Set to TRUE only when live creds are available
)
```

## Overview

This vignette covers:

1. **Live market data** — browsing markets, orderbooks, recent trades
2. **Candlestick charts** — OHLCV data for price history
3. **Historical endpoints** — data before the cutoff date
4. **Pagination** — handling large result sets with cursors

---

## Setup

```{r auth}
library(kalshiR)
library(dplyr)
library(ggplot2)

kalshi_set_auth(kalshi_auth(
  key_id      = Sys.getenv("KALSHI_KEY_ID"),
  private_key = Sys.getenv("KALSHI_KEY_PATH")
))
```

---

## 1. Browsing Markets

### List open markets

```{r list-markets}
# First 50 open markets
markets <- get_markets(status = "open", limit = 50L)
glimpse(markets)
```

`get_markets()` returns a tibble with one row per market. Key columns:

| Column | Description |
|--------|-------------|
| `ticker` | Unique market identifier |
| `title` | Human-readable market question |
| `status` | `"open"`, `"closed"`, `"settled"` |
| `yes_bid` | Best yes bid (cents) |
| `yes_ask` | Best yes ask (cents) |
| `last_price` | Last traded price (cents) |
| `volume` | Total volume (contracts) |
| `close_time` | When the market closes (POSIXct UTC) |

### Filter by series or event

```{r filter-markets}
# All markets in the INXD series (S&P 500 daily)
sp500_markets <- get_markets(series_ticker = "INXD", status = "open")
sp500_markets |>
  select(ticker, title, yes_bid, yes_ask, volume) |>
  arrange(desc(volume))
```

### Get all pages at once

By default, `get_markets()` returns at most `limit` results. Use
`all_pages = TRUE` to follow cursors automatically:

```{r all-pages}
# WARNING: may return thousands of rows
all_markets <- get_markets(status = "open", all_pages = TRUE)
nrow(all_markets)
```

> **Tip**: Always start with a small `limit` to check the data shape
> before requesting `all_pages = TRUE`.

---

## 2. Single Market Detail

```{r single-market}
mkt <- get_market("INXD-23DEC29-B4900")
glimpse(mkt)
```

---

## 3. Orderbook

The orderbook shows the current buy/sell interest at each price level.

```{r orderbook}
ob <- get_orderbook("INXD-23DEC29-B4900")
# ob is a list with two data frames: $yes and $no
ob$yes   # yes-side bids (sorted best → worst)
ob$no    # no-side bids
```

Visualise the orderbook depth:

```{r orderbook-plot}
# Combine both sides for a depth chart
yes_side <- ob$yes |> mutate(side = "yes")
no_side  <- ob$no  |> mutate(side = "no")
depth    <- bind_rows(yes_side, no_side)

ggplot(depth, aes(x = price, y = cumsum(quantity), colour = side)) +
  geom_step() +
  scale_colour_manual(values = c(yes = "#2ecc71", no = "#e74c3c")) +
  labs(title = "Order Book Depth", x = "Price (cents)", y = "Cumulative Contracts") +
  theme_minimal()
```

---

## 4. Recent Public Trades

```{r recent-trades}
trades <- get_trades("INXD-23DEC29-B4900", limit = 100L)
glimpse(trades)

# Volume-weighted average price of last 100 trades
trades |>
  summarise(
    vwap   = sum(yes_price * count) / sum(count),
    volume = sum(count)
  )
```

---

## 5. Candlestick Charts

`get_market_candlesticks()` returns OHLCV data for a market. The
`period_interval` is in **minutes** (e.g. `60L` = hourly candles).

```{r candlesticks}
candles <- get_market_candlesticks(
  series_ticker   = "INXD",
  ticker          = "INXD-23DEC29-B4900",
  period_interval = 60L,         # 60-minute candles
  start_ts        = Sys.time() - 7 * 24 * 3600,   # last 7 days
  end_ts          = Sys.time()
)
glimpse(candles)
```

Returned columns include `end_period_ts` (POSIXct), `price_open`,
`price_high`, `price_low`, `price_close`, and `volume`.

### OHLC candlestick chart

```{r ohlc-chart}
ggplot(candles, aes(x = end_period_ts)) +
  # High-low wicks
  geom_linerange(
    aes(ymin = price_low, ymax = price_high),
    colour = "grey60", linewidth = 0.5
  ) +
  # Open-close body
  geom_segment(
    aes(
      xend   = end_period_ts,
      y      = price_open,
      yend   = price_close,
      colour = price_close >= price_open
    ),
    linewidth = 2
  ) +
  scale_colour_manual(
    values = c("TRUE" = "#2ecc71", "FALSE" = "#e74c3c"),
    guide  = "none"
  ) +
  labs(
    title = "INXD-23DEC29-B4900 — Hourly Candles",
    x     = NULL,
    y     = "Price (cents)"
  ) +
  theme_minimal()
```

### Volume bar chart

```{r volume-chart}
ggplot(candles, aes(x = end_period_ts, y = volume)) +
  geom_col(fill = "#3498db", alpha = 0.7) +
  labs(title = "Hourly Volume", x = NULL, y = "Contracts") +
  theme_minimal()
```

---

## 6. Historical Data

Kalshi maintains a **historical cutoff date**. Data older than the cutoff
must be queried via `/historical/...` endpoints.

```{r historical-cutoff}
cutoff <- get_historical_cutoff()
cutoff$cutoff_ts   # POSIXct — data older than this → use historical endpoints
```

### Historical markets (resolved/expired)

```{r historical-markets}
old_markets <- get_historical_markets(
  series_ticker = "INXD",
  limit         = 100L
)
glimpse(old_markets)
```

### Historical candlesticks

```{r historical-candles}
hist_candles <- get_historical_candlesticks(
  series_ticker   = "INXD",
  ticker          = "INXD-23NOV30-B4500",
  period_interval = 1440L,   # daily candles
  start_ts        = "2023-11-01T00:00:00Z",
  end_ts          = "2023-11-30T23:59:59Z"
)
glimpse(hist_candles)
```

### Historical public trades

```{r historical-trades}
hist_trades <- get_historical_trades(
  ticker   = "INXD-23NOV30-B4500",
  limit    = 500L,
  all_pages = TRUE
)
nrow(hist_trades)
```

---

## 7. Pagination Patterns

All list functions share the same cursor-based pagination interface.

### Manual pagination

```{r manual-pagination}
# Page 1
page1 <- get_markets(status = "open", limit = 10L)
cursor <- attr(page1, "next_cursor")   # NULL if no more pages

# Page 2 (if cursor is not NULL)
if (!is.null(cursor)) {
  page2 <- get_markets(status = "open", limit = 10L, cursor = cursor)
}
```

### Automatic pagination

```{r auto-pagination}
# kalshi_paginate() is used internally by all list functions
# when all_pages = TRUE
all_events <- get_events(all_pages = TRUE)
message("Total events fetched: ", nrow(all_events))
```

### Chunked pagination for large datasets

When you want all results but want to process them in chunks (to avoid
memory issues or to show progress):

```{r chunked}
# Use the cursor manually to stream results
results <- list()
cursor  <- NULL

repeat {
  page   <- get_trades("INXD-23DEC29-B4900",
                        limit  = 100L,
                        cursor = cursor)
  results <- c(results, list(page))

  cursor <- attr(page, "next_cursor")
  if (is.null(cursor) || nrow(page) == 0L) break
}

all_trades <- dplyr::bind_rows(results)
nrow(all_trades)
```

---

## Summary

| Data type | Live endpoint | Historical endpoint |
|-----------|---------------|---------------------|
| Markets | `get_markets()` | `get_historical_markets()` |
| Candlesticks | `get_market_candlesticks()` | `get_historical_candlesticks()` |
| Public trades | `get_trades()` | `get_historical_trades()` |
| Your fills | `get_fills()` | `get_historical_fills()` |
| Your orders | `get_orders()` | `get_historical_orders()` |

Use `get_historical_cutoff()` to determine which endpoint applies for
a given time range.
