---
title: "Trading: Orders, Positions, and Fills"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trading: Orders, Positions, and Fills}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  eval     = FALSE
)
```

> ⚠️ **Important**: The code in this vignette places real orders and
> moves real money. Use the **demo environment** while learning.
> See `vignette("getting-started")` for demo setup instructions.

## Overview

This vignette covers the full trading workflow:

1. Checking your balance
2. Placing limit and market orders
3. Monitoring and amending open orders
4. Cancelling orders
5. Viewing positions and fills
6. Batch operations

---

## Setup (Demo Environment)

```{r auth}
library(kalshiR)
library(dplyr)

# Always test with demo credentials first
demo_creds <- demo_creds()
```

---

## 1. Check Your Balance

```{r balance}
bal <- get_balance()
print(bal)
# # A tibble: 1 × 3
#   available_balance portfolio_value bonus_balance
#               <dbl>           <dbl>         <dbl>
# 1             498.3            12.5             0
```

All values are in **dollars** (kalshiR converts from the API's cent values).

- `available_balance`: Cash you can use to place new orders.
- `portfolio_value`: Mark-to-market value of your open positions.
- `bonus_balance`: Promotional credit (cannot be withdrawn).

---

## 2. Placing Orders

### Limit orders

A limit order fills only at your specified price or better. You pay the
price upfront (for yes) or `100 - price` (for no).

```{r limit-order}
# Buy 5 "yes" contracts at 30 cents each
# Cost = 5 × $0.30 = $1.50 (deducted from available_balance immediately)
order <- create_order(
  ticker    = "INXD-23DEC29-B4900",
  side      = "yes",
  type      = "limit",
  count     = 5L,
  yes_price = 30L    # integer cents, 1–99
)

print(order)
# # A tibble: 1 × 10
#   order_id   ticker               status  yes_price no_price type  side  count remaining_count created_time
#   <chr>      <chr>                <chr>       <int>    <int> <chr> <chr> <int>           <int> <dttm>
# 1 ord-abc123 INXD-23DEC29-B4900  resting        30       NA limit yes       5               5 2024-03-01...
```

> **Price convention**: For a yes-limit order, specify `yes_price`.
> For a no-limit order, specify `no_price`. You cannot specify both.

### Market orders

A market order fills immediately at the best available price. Do **not**
specify a price for market orders.

```{r market-order}
# Buy 1 "yes" at market (fills at current best ask)
market_order <- create_order(
  ticker = "INXD-23DEC29-B4900",
  side   = "yes",
  type   = "market",
  count  = 1L
)
```

> **Warning**: Market orders on low-liquidity markets may fill at
> unfavourable prices. Check the orderbook first with `get_orderbook()`.

---

## 3. Monitoring Orders

### List open orders

```{r get-orders}
open_orders <- get_orders(status = "resting")
open_orders |>
  select(order_id, ticker, side, yes_price, no_price, count, remaining_count)
```

### Get a specific order

```{r get-order}
order_id <- order$order_id
latest   <- get_order(order_id)
latest$status           # "resting", "filled", "cancelled", etc.
latest$remaining_count  # contracts still open
```

### Full order lifecycle poll

```{r poll-order}
# Poll until filled or 60 seconds elapsed
deadline <- Sys.time() + 60

repeat {
  latest <- get_order(order_id)
  if (latest$status != "resting") break
  if (Sys.time() > deadline) {
    message("Order still resting after 60s")
    break
  }
  Sys.sleep(2)
}

message("Final status: ", latest$status)
```

---

## 4. Amending Orders

You can change the price or quantity of a resting order without cancelling
and re-submitting. At least one of `yes_price`, `no_price`, or `count`
must be supplied.

```{r amend-order}
# Lower the price (less aggressive bid)
amended <- amend_order(
  order_id  = order_id,
  yes_price = 25L    # was 30
)
amended$yes_price   # 25
```

### Decrease order size

To reduce quantity only (without changing price), use `decrease_order()`:

```{r decrease-order}
# Reduce from 5 to 3 contracts (reduce_by = 2)
smaller <- decrease_order(order_id = order_id, reduce_by = 2L)
smaller$remaining_count   # should be 3
```

---

## 5. Cancelling Orders

```{r cancel-order}
cancelled <- cancel_order(order_id)
cancelled$status   # "cancelled"
```

### Cancel all open orders for a market

```{r cancel-all}
to_cancel <- get_orders(
  ticker = "INXD-23DEC29-B4900",
  status = "resting"
)

for (oid in to_cancel$order_id) {
  tryCatch(
    cancel_order(oid),
    error = function(e) message("Could not cancel ", oid, ": ", e$message)
  )
}
```

---

## 6. Positions and Fills

### Current positions

```{r positions}
positions <- get_positions(settled = FALSE)
positions |>
  select(ticker, position, market_exposure, realized_pnl, unrealized_pnl)
```

Column meanings:

| Column | Description |
|--------|-------------|
| `position` | Net contracts held (positive = long yes, negative = long no) |
| `market_exposure` | Cash at risk (dollars) |
| `realized_pnl` | Profit/loss on closed contracts (dollars) |
| `unrealized_pnl` | Mark-to-market P&L on open contracts (dollars) |

### Recent fills

```{r fills}
fills <- get_fills(limit = 50L)
fills |>
  select(fill_id, ticker, side, yes_price, count, created_time) |>
  arrange(desc(created_time))
```

### P&L summary

```{r pnl}
fills |>
  group_by(ticker) |>
  summarise(
    total_contracts = sum(count),
    avg_price       = weighted.mean(yes_price, count),
    .groups         = "drop"
  ) |>
  arrange(desc(total_contracts))
```

---

## 7. Settlements

When a market resolves, your contracts are settled and cash is credited
(or debited). View settlement history:

```{r settlements}
settlements <- get_settlements(limit = 100L)
settlements |>
  select(ticker, side, count, yes_price, revenue, settled_time) |>
  filter(revenue > 0) |>
  arrange(desc(settled_time))
```

Each row represents a settled position. `revenue` is the dollar amount
credited to your account.

---

## 8. Batch Operations

For high-frequency use cases, kalshiR supports placing and cancelling
up to **20 orders** in a single API call.

### Batch create

```{r batch-create}
# Build a list of order specifications
orders_to_place <- list(
  list(
    ticker    = "INXD-23DEC29-B4900",
    side      = "yes",
    type      = "limit",
    count     = 2L,
    yes_price = 28L
  ),
  list(
    ticker    = "INXD-23DEC29-B4950",
    side      = "no",
    type      = "limit",
    count     = 1L,
    no_price  = 35L
  )
)

batch_result <- batch_create_orders(orders_to_place)
print(batch_result)
# # A tibble: 2 × 10
#   order_id   ticker               status  ...
```

### Batch cancel

```{r batch-cancel}
# Cancel the orders we just placed
ids_to_cancel <- batch_result$order_id

batch_cancelled <- batch_cancel_orders(ids_to_cancel)
all(batch_cancelled$status == "cancelled")  # TRUE
```

---

## 9. Full Trade Example

Here is a complete end-to-end example on the demo environment:

```{r full-example}
library(kalshiR)
library(dplyr)

# 1. Auth
kalshi_set_auth(kalshi_auth(
  key_id      = Sys.getenv("KALSHI_DEMO_KEY_ID"),
  private_key = Sys.getenv("KALSHI_DEMO_KEY_PATH"),
  env         = "demo"
))

# 2. Find an open market
markets <- get_markets(status = "open", limit = 5L)
ticker  <- markets$ticker[[1]]
message("Trading: ", ticker)

# 3. Check the orderbook
ob <- get_orderbook(ticker)
best_yes_ask <- ob$yes$price[[1]]   # lowest ask = best price to buy yes
message("Best yes ask: ", best_yes_ask, " cents")

# 4. Check balance before
bal_before <- get_balance()
message("Balance before: $", round(bal_before$available_balance, 2))

# 5. Place a conservative limit order (bid well below market)
order <- create_order(
  ticker    = ticker,
  side      = "yes",
  type      = "limit",
  count     = 1L,
  yes_price = max(1L, as.integer(best_yes_ask) - 10L)  # 10 cents below ask
)
message("Order placed: ", order$order_id, " (status: ", order$status, ")")

# 6. Wait a moment, check status
Sys.sleep(3)
updated <- get_order(order$order_id)
message("Order status after 3s: ", updated$status)

# 7. Cancel if still resting
if (updated$status == "resting") {
  cancelled <- cancel_order(order$order_id)
  message("Cancelled. Final status: ", cancelled$status)
}

# 8. Balance after (should be unchanged since order didn't fill)
bal_after <- get_balance()
message("Balance after: $", round(bal_after$available_balance, 2))
```

---

## Error Handling

kalshiR surfaces API errors as R conditions. Common errors:

| HTTP Status | Meaning | Typical cause |
|-------------|---------|---------------|
| 400 | Bad request | Invalid order params (price out of range, etc.) |
| 401 | Unauthorised | Bad key ID or invalid signature |
| 403 | Forbidden | Attempting to trade a closed market |
| 404 | Not found | Invalid ticker or order ID |
| 429 | Rate limited | Too many requests |

```{r error-handling}
result <- tryCatch(
  create_order(
    ticker    = ticker,
    side      = "yes",
    type      = "limit",
    count     = 1L,
    yes_price = 50L
  ),
  httr2_http_400 = function(e) {
    message("Bad request: ", conditionMessage(e))
    NULL
  },
  httr2_http_429 = function(e) {
    message("Rate limited — wait a moment and retry")
    NULL
  }
)
```
